Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds

### 2016-02-08 paper.tex
modded names

\author[Matthews et al.]{
\parbox[t]{\textwidth}{
James~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, Christian~Knigge$^1$, 
Knox~S.~Long$^2$, Stuart~A.~Sim$^3$, Nick~Higginbottom$^1$ and Sam~W.~Mangham$^1$
}
\medskip  
\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom
\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD, 21218
\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK
}

>>>>

\author[Matthews et al.]{
\parbox[t]{\textwidth}{
J.~H.~Matthews$^1$\thanks{jm8g08@soton.ac.uk}, C.~Knigge$^1$, 
K.~S.~Long$^2$, S.~A.~Sim$^3$, N.~Higginbottom$^1$ and S.~W.~Mangham$^1$
}
\medskip  
\\$^1$School of Physics and Astronomy, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom
\\$^2$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD, 21218
\\$^3$School of Mathematics and Physics, Queens University Belfast, University Road, Belfast, BT7 1NN, Northern Ireland, UK
}
